---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

# nsyllable

<!-- badges: start -->
[![CRAN Version](https://www.r-pkg.org/badges/version/nsyllable)](https://CRAN.R-project.org/package=nsyllable)
`r badge_devel("quanteda/nsyllable", "royalblue")`
[![Downloads](https://cranlogs.r-pkg.org/badges/nsyllable)](https://CRAN.R-project.org/package=nsyllable)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/nsyllable?color=orange)](https://CRAN.R-project.org/package=nsyllable)
[![R build status](https://github.com/quanteda/nsyllable/workflows/R-CMD-check/badge.svg)](https://github.com/quanteda/nsyllable/actions)
[![codecov](https://codecov.io/gh/quanteda/nsyllable/branch/master/graph/badge.svg)](https://codecov.io/gh/quanteda/nsyllable)
<!-- badges: end -->

## About

Counts syllables in character vectors for English words, based on the [Carnegie
Mellon University Pronouncing
Dictionary](http://www.speech.cs.cmu.edu/cgi-bin/cmudict).  Imputes syllables as
the number of vowel sequences for words not found.

We hope to add more languages soon.

## How to Install

Currently, **nsyllable** is currently only on GitHub.  To install:
```{r eval = FALSE}
# devtools package required to install nsyllable from Github 
devtools::install_github("quanteda/nsyllable") 
```

## Demonstration

```{r}
library("nsyllable")

charvec <- c("testing", "Aachen", "supercalifragilisticexpialidocious")
nsyllable(charvec)
nsyllable(charvec, use.names = TRUE)
```


