---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```
```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

# nsyllable

<!-- badges: start -->
[![CRAN Version](https://www.r-pkg.org/badges/version/nsyllable)](https://CRAN.R-project.org/package=nsyllable)
`r badge_devel("quanteda/nsyllable", "royalblue")`
[![Downloads](https://cranlogs.r-pkg.org/badges/nsyllable)](https://CRAN.R-project.org/package=nsyllable)
[![Total Downloads](https://cranlogs.r-pkg.org/badges/grand-total/nsyllable?color=orange)](https://CRAN.R-project.org/package=nsyllable)
[![R build status](https://github.com/quanteda/nsyllable/workflows/R-CMD-check/badge.svg)](https://github.com/quanteda/nsyllable/actions)
[![codecov](https://codecov.io/gh/quanteda/nsyllable/branch/master/graph/badge.svg)](https://app.codecov.io/gh/quanteda/nsyllable)
<!-- badges: end -->

## About

Counts syllables in character vectors.  For English, this looks up syllables
from the [Carnegie Mellon University Pronouncing
Dictionary](http://www.speech.cs.cmu.edu/cgi-bin/cmudict), or guesses the
syllables as the number of vowel sequences for words not found.  User-supplied
syllable word lists are also supported.

We hope to add lookup tables for additional languages in the future.

## How to Install

From CRAN:
```{r eval = FALSE}
install.packages("nsyllable")
```

From GitHub:
```{r eval = FALSE}
# remotes package required to install nsyllable from Github 
remotes::install_github("quanteda/nsyllable") 
```

## Usage

`nsyllable()` counts the syllables in each element of a character vector, and returns the integer vector of the syllable counts.  If `use.names = TRUE`, then the output vector is named.  The default (and currently, only) language implemented is English.

```{r}
library("nsyllable")

charvec <- c("testing", "Aachen", "supercalifragilisticexpialidocious")
nsyllable(charvec)
nsyllable(charvec, use.names = TRUE)
```

User-supplied dictionaries can also be used, and these will override the `language` argument.  Below, "excellent" is still (correctly) counted, but not because it looked up the results in the English dictionary, but because it counted the vowel sequences.  This gets "noel" wrong, however.
```{r}
nsyllable(c("excellent", "noel", "film"), use.names = TRUE)

# redefine the syllables as it's pronounced in parts of Ireland
mydict <- c("film" = 2L)
# looks up "excellent" and does the vowel count
nsyllable(c("excellent", "noel", "film"), syllable_dictionary = mydict, use.names = TRUE)
```

To not use the English dictionary and count only vowel sequences, set `syllable_dictionary` to `NULL`.  This will likely to be a good approximation for many Western languages.
```{r}
nsyllable(c("Dies", "ist", "eine", "Demonstration"), syllable_dictionary = NULL,
          use.names = TRUE)
```


